Exploration of the MIRT solutions

### 2024-02-02 notebooks/Mirt_solution_exploration.Rmd
Changes the sourcing of R file so that it works independently of knitting directory
Improves notebook output to make it clearer

---
title: 'Exploration of the MIRT solutions'
output:
  html_document: 
    df_print:        paged
    code_folding:    show
    toc:             yes
    toc_float:       yes
editor_options: 
  chunk_output_type: console
---

```{r setup}
library(knitr)
library(mirt)
library(tidyverse)

source('R/Mirt_toolbox.R', encoding = 'UTF-8')

@@

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = TRUE,
  message  = FALSE,
  cache    = FALSE
)

@@

@@

```{r fit-model}
data <- expand.table(LSAT7)
itemstats(data)

mod2 <- mirt(data, 2)
coef(mod2)
summary(mod2, rotate = 'oblimin') #oblimin rotation
```

@@

```{r param-equivalence}
sum <- summary(mod2, rotate = 'oblimin') #oblimin rotation
sum$rotF |> as_tibble() |> mutate(
  across(everything(), ~1.702 * . / sqrt(1-as.numeric(sum$h2)))
)
```

>>>>

---
title: 'Exploration of the MIRT solutions'
output:
  html_document: 
    df_print:        paged
    code_folding:    show
    toc:             yes
    toc_float:       yes
editor_options: 
  chunk_output_type: inline
---

```{r setup}
#| message: false
library(knitr)
library(mirt)
library(tidyverse)

@@

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = TRUE,
  message  = FALSE,
  cache    = FALSE,
  results  = 'hold'
)

@@

```{r sources}
source('R/Mirt_toolbox.R', encoding = 'UTF-8')
```

@@

```{r fit-model}
#| message: false
data <- expand.table(LSAT7)
itemstats(data)

mod2 <- mirt(data, 2, verbose = FALSE)
coef(mod2)
summary(mod2, rotate = 'oblimin') #oblimin rotation
```

@@

```{r param-equivalence}
sum <- summary(mod2, rotate = 'oblimin') #oblimin rotation
sum$rotF      |>
  as_tibble() |>
  mutate(
    across(everything(), ~1.702 * . / sqrt(1-as.numeric(sum$h2)))
  )           |>
  # Update the column names so they refer correctly to the discrimination
  #   parameters instead of the factor loadings.
  rename_with(str_replace, everything(), pattern = 'F', replacement = 'a')
```
